---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

[![lifecycle](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)

> Disclaimer: this package is still at an experimental level, and should only be used for testing, bug reports, and enhancement requests. As long as this package is in "Experimental" mode, some changes to the API are to be expected. Read the [NEWS.md](NEWS.md) to be informed of the last changes.

This package has only been tested on these platforms for now, so it might not work on others : 

- neo4j 3.3.3

  + Mac OSX

# run4j

The goal of run4j is to facilitate Neo4J orchestration from R. 

## Installation

You can install {run4j} from GitHub with:

```{r gh-installation, eval = FALSE}
# install.packages("remotes")
remotes::install_github("ThinkR-open/play4j")
```

## Example

### Casual Neo4J Orchestration

+ Create an instance with `neo4j_shell$new` and the path to your `NEO4JHOME`:

```{r}
cypher_con <- run4j::neo4j_shell$new("/Users/colin/neo4j/")
```

+ Start Neo4J : 

```{r}
# In the background
cypher_con$start()
# In the front
cypher_con$console()
```

+ Make cypher call 

You can make cypher call with the cypher method : 

```{r}
cypher_con$cypher(cypher = "MATCH (n) RETURN n LIMIT 5;",
          username = "neo4j", password = "pouetpouet", format = "plain")
```


+ Restart Neo4J :  

```{r}
cypher_con$restart()
```

+ See logs and certificates list : 

```{r}
# See the last 5 lines
cypher_con$see_logs(size = 5)
cypher_con$see_certificates()
```

You can also see plugins, imports, data and run.

+ See status 

```{r}
cypher_con$status()
```

+ Get Neo4J version

```{r}
cypher_con$version()
```

+ Stop Neo4J

```{r}
cypher_con$stop()
```

### Neo4J API Calls

If you simply want to make API calls, start a new `neo4j_api` object: 

```{r}
api_con <- run4j::neo4j_api$new(url = "http://localhost:7474", user = "neo4j", password = "pouetpouet")
```

Then query (result as JSON or as an R list):

```{r}
# As JSON (default)
api_con$query("MATCH (p:Person) RETURN p.name LIMIT 1")
# As R list 
api_con$query("MATCH (p:Person) RETURN p.name LIMIT 1", format = "R")
```

### Neo4J Admin Orchestration

You can call [Neo4J admin commands](https://neo4j.com/docs/operations-manual/current/tools/neo4j-admin/) by creating a new neo4j_admin object:

```{r}
admin <- run4j::neo4j_admin$new("/Users/colin/neo4j/")
```

You can call admin commands with args that looks like shell commands (i.e. you should type `args = "--verbose true"`, for example).

```{r}
admin$memrec()
```

Every admin method comes with a `help` arg, that can be turned on to get the list of args to pass to the commands. 

```{r}
admin$check_consistency(help = TRUE)
```


  Please note that this project is released with a [Contributor Code of Conduct](CODE_OF_CONDUCT.md).
  By participating in this project you agree to abide by its terms.
